Anonymizing ids

### 2021-06-11 text/21/anonymizing-ids.Rmd
Completed anonymizing_ids

---
title: "Anonymizing ids"
author: "Steve Simon"
source: "New"
date: "2020-04-15"
categories:
- Blog post
tags:
- Privacy in research
output: html_document
---

@@

2. Add the same random number to each eight digit id. This will produce a new nine digit id.

@@

### 2. Add the same random number to each eight digit id. This will produce a new nine digit id.

@@

```{r, echo=FALSE}
library(knitr)
x <- rep(c(12345678, 23456789, 34567890), c(4, 3, 2))
kable(x)
```

Here's what those ID numbers look like when you add my random number

```{r, echo=FALSE}
kable(data.frame(x=x, y=x+480035489))
```

>>>>

---
title: "Anonymizing ids"
author: "Steve Simon"
source: "New"
date: "2020-06-10"
categories:
- Blog post
tags:
- Privacy in research
output: html_document
---

@@

2. Add the same random number to each eight digit id.

@@

There is a complication in Microsoft Excel that you have to work around. The randbetween function will recalculate everytime you make a change anywhere else in the workbook. You need to "freeze" the random number by copying and pasting it to a different cell using the "past values" option under "paste special."

### 2. Add the same random number to each eight digit id.

@@

```{r, echo=FALSE}
suppressMessages(suppressWarnings(library(dplyr)))
suppressMessages(suppressWarnings(library(knitr)))
suppressMessages(suppressWarnings(library(kableExtra)))
suppressMessages(suppressWarnings(library(magrittr)))
private_id <- 12345678+(0:7)*11262783
data.frame(private_id=private_id) %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

Here's what those ID numbers look like when you add my random number. We now have a random nine digit id associated with each eight digit id.

```{r, echo=FALSE}
e <- data.frame(private_id=as.character(private_id), random_id=as.character(private_id+480035489))

e %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

### 3. Link the eight and nine digit ids to the raw data.

Here's the file with the actual data and the private ID code

```{r, echo=FALSE}
d <- data.frame(
  private_id=c(rep(private_id[1:3], c(4, 3, 2)), "..."),
  report_date=c(as.character(Sys.Date()-round(runif(9, 0, 60))), "..."),
  data=c(round(runif(9, 100, 199)), "..."))
d %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

Merge the two files together.

```{r, echo=FALSE}
e %>%
  bind_rows(data.frame(private_id="...", random_id="...")) -> f
merge(f, d) -> g
# g <- g[c(2:9, 1), ]
h <- g[c(2:9, 1), ]
h %>%
  tibble %>%
  data.frame %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

### 4. Store the merged data with the nine digit id, but not the eight digit id.

You now have a new random_id in place of the private id.

```{r, echo=FALSE}
h %>%
  select(-private_id) %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

### 5. Shred the random number.

Once the random number is destroyed, the nine digit id cannot be converted back to the eight digit id.
